\subsection{GraspIt! Installation - Linux}

\subsubsection{Qt}

Download Qt for C++ from the \xlink{Qt
  website}{http://www.qtsoftware.com/downloads}.

Follow the installation instructions (this usually amounts to just
doing \texttt{configure} and \texttt{make}). The installation
automatically goes to \texttt{/usr/local/Trolltech/Qt-4.4.3}, unless
you specify a different installation path. Set the following
environment variables:

\begin{itemize}
\item \texttt{QTDIR} - the path to your Qt installation 
\item \texttt{PATH} - add the path to \texttt{\$QTDIR/bin}
\end{itemize}

On Ubuntu systems it is probably possible to get Qt from the package
manager. We have not tested this, but you will probably need all of
the following packages:

\begin{itemize}
\item libqt4-core
\item libqt4-debug
\item libqt4-dev
\item libqt4-gui
\item libqt4-qt3support
\end{itemize}

\subsubsection{Coin}

Download Coin3d from the \xlink{Coin3D website}{www.coin3d.org} and
follow installation instructions. The examples below assume you choose
to install Coin in \texttt{/usr/local/Coin} (i.e. use
\texttt{configure~--prefix=/usr/local/Coin}). Set the following
environment variables:

\begin{itemize}
\item \texttt{COINDIR} - the directory where you installed Coin
  (e.g. \texttt{/usr/local/Coin})
\item \texttt{PATH} - add \texttt{\$COINDDIR/bin}
  (e.g. \texttt{/usr/local/Coin/bin})
\item \texttt{LD\_LIBRARY\_PATH} - add \texttt{\$COINDIR/lib}
  (e.g. \texttt{/usr/local/Coin/lib})
\end{itemize}

\subsubsection{SoQt}

Download SoQt from the \xlink{Coin3D website}{http://www.coin3d.org}
and follow the installation instruction. The configure script needs
the path to your Coin installation -
e.g. \texttt{configure~--prefix=/usr/local/Coin}. Then just type
\texttt{make install}.

\subsubsection{Lapack}

On Ubuntu, all you need to do is install the following packages form
the package manager:
\begin{itemize}
\item libblas-dev
\item liblapack-dev
\end{itemize}

\subsubsection{GraspIt!}

Download and unzip the GraspIt! code itself. Set the following
environment variable:

\begin{itemize}
\item \texttt{GRASPIT} - the directory where you unzipped GraspIt!
\end{itemize}

Build QHull. Go to the \texttt{\$GRASPIT/qhull} directory and type
\texttt{make}.

Create the GraspIt! Makefile from the Qt project file. Edit
\texttt{\$GRASPIT/graspit.pro} to suit your system and
installation needs. Then type \texttt{qmake graspit.pro}.

Build and go. From \texttt{\$GRASPIT/} type \texttt{make}.
